\subsection{Graphics.ChalkBoard.Utils}     

         

 

 
\begin{tabular}{p{0.95\linewidth}}{\bf {\bf Contents}}\\ % (8)

 
\begin{itemize}
\setlength{\itemsep}{0in}

\item Point Utilties.
\item Utilties for {\tt R}.
\end{itemize}
\\ % (30)


\end{tabular}


 

\subsubsection{Description}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}This module has some basic, externally visable, definitions.\end{minipage}

 

\subsubsection{Synopsis}

 

 
\begin{tabular}{p{0.95\linewidth}}{insideRegion :: (Point, Point) -{\tt >} Point -{\tt >} Bool}\\ % (59)


{insideCircle :: Point -{\tt >} R -{\tt >} Point -{\tt >} Bool}\\ % (61)


{distance :: Point -{\tt >} Point -{\tt >} R}\\ % (43)


{intervalOnLine :: (Point, Point) -{\tt >} Point -{\tt >} R}\\ % (58)


{circleOfDots :: Int -{\tt >} [Point]}\\ % (36)


{insidePoly :: [Point] -{\tt >} Point -{\tt >} Bool}\\ % (50)


{innerSteps :: Int -{\tt >} [R]}\\ % (30)


{outerSteps :: Int -{\tt >} [R]}\\ % (30)


{fracPart :: R -{\tt >} R}\\ % (24)


{fromPolar :: (R, Radian) -{\tt >} Point}\\ % (39)


{toPolar :: Point -{\tt >} (R, Radian)}\\ % (37)


{angleOfLine :: (Point, Point) -{\tt >} Radian}\\ % (45)


\end{tabular}


 

 

\subsubsection{Point Utilties.}

 

{{\bf insideRegion} :: (Point, Point) -{\tt >} Point -{\tt >} Bool}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}is a {\tt Point} inside a region?\end{minipage}

 

{{\bf insideCircle} :: Point -{\tt >} R -{\tt >} Point -{\tt >} Bool}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}is a {\tt Point} inside a circle, where the first two arguments are the center of the circle, and the radius.
\end{minipage}

 

{{\bf distance} :: Point -{\tt >} Point -{\tt >} R}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}What is the {\tt distance} between two points in R2? This is optimised for the normal form {\tt distance p1 p2 {\tt <}= v}, which avoids using {\tt sqrt}.\end{minipage}

 

{{\bf intervalOnLine} :: (Point, Point) -{\tt >} Point -{\tt >} R}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}{\tt intervalOnLine} find the place on a line (between 0 and 1) that is closest to the given point.\end{minipage}

 

{{\bf circleOfDots} :: Int -{\tt >} [Point]}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}circleOfDots generates a set of points between (-1..1,-1..1), inside a circle.\end{minipage}

 

{{\bf insidePoly} :: [Point] -{\tt >} Point -{\tt >} Bool}

 

\subsubsection{Utilties for {\tt R}.}

 

{{\bf innerSteps} :: Int -{\tt >} [R]}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}innerSteps takes n even steps from 0 .. 1, by not actually touching 0 or 1. The first and last step are 1/2 the size of the others, so that repeated innerSteps
 can be tiled neatly.
\end{minipage}

 

{{\bf outerSteps} :: Int -{\tt >} [R]}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}outerSteps takes n even steps from 0 .. 1, starting with 0, and ending with 1,  returning n+1 elements.
\end{minipage}

 

{{\bf fracPart} :: R -{\tt >} R}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}Extract the fractional part of an {\tt R}.\end{minipage}

 

{{\bf fromPolar} :: (R, Radian) -{\tt >} Point}

 

{{\bf toPolar} :: Point -{\tt >} (R, Radian)}

 

{{\bf angleOfLine} :: (Point, Point) -{\tt >} Radian}

 

 

