\subsection{Graphics.ChalkBoard.Main}     

  

 

 

\subsubsection{Synopsis}

 

 
\begin{tabular}{p{0.95\linewidth}}{data  ChalkBoard }\\ % (17)


{drawChalkBoard :: ChalkBoard -{\tt >} Board RGB -{\tt >} IO ()}\\ % (62)


{writeChalkBoard :: ChalkBoard -{\tt >} FilePath -{\tt >} IO ()}\\ % (62)


{updateChalkBoard :: ChalkBoard -{\tt >} (Board RGB -{\tt >} Board RGB) -{\tt >} IO ()}\\ % (85)


{drawRawChalkBoard :: ChalkBoard -{\tt >} [Inst BufferId] -{\tt >} IO ()}\\ % (71)


{exitChalkBoard :: ChalkBoard -{\tt >} IO ()}\\ % (43)


{startChalkBoard :: [Options] -{\tt >} (ChalkBoard -{\tt >} IO ()) -{\tt >} IO ()}\\ % (80)


{openChalkBoard :: [Options] -{\tt >} IO ChalkBoard}\\ % (50)


{chalkBoardServer :: IO ()}\\ % (25)


\end{tabular}


 

\subsubsection{Documentation}

 

{data  {\bf ChalkBoard}  }

 

{{\bf drawChalkBoard} :: ChalkBoard -{\tt >} Board RGB -{\tt >} IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}Draw a board onto the ChalkBoard.\end{minipage}

 

{{\bf writeChalkBoard} :: ChalkBoard -{\tt >} FilePath -{\tt >} IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}Write the contents of a ChalkBoard into a File.\end{minipage}

 

{{\bf updateChalkBoard} :: ChalkBoard -{\tt >} (Board RGB -{\tt >} Board RGB) -{\tt >} IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}modify the current ChalkBoard.\end{minipage}

 

{{\bf drawRawChalkBoard} :: ChalkBoard -{\tt >} [Inst BufferId] -{\tt >} IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}Debugging hook for writing raw CBIR code.\end{minipage}

 

{{\bf exitChalkBoard} :: ChalkBoard -{\tt >} IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}quit ChalkBoard.\end{minipage}

 

{{\bf startChalkBoard} :: [Options] -{\tt >} (ChalkBoard -{\tt >} IO ()) -{\tt >} IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}Start, in this process, a ChalkBoard window, and run some commands on it.\end{minipage}

 

{{\bf openChalkBoard} :: [Options] -{\tt >} IO ChalkBoard}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}Open, remotely, a ChalkBoard windown, and return a handle to it. Needs CHALKBOARD\_SERVER set to the location of the ChalkBoard server.\end{minipage}

 

{{\bf chalkBoardServer} :: IO ()}

\hspace{0.05\textwidth}\begin{minipage}{0.9\textwidth}create an instance of the ChalkBoard. Only used by the server binary.\end{minipage}

 

 

